R for Clinical Study Reports and Submission

### 2022-08-12 tlf-assemble.Rmd
add ad-hoc functions.

```{r, include=FALSE}
#' Assemble RTF files into one single RTF file 
#' 
#' @param path a vector of RTF file path
#' 
#' @export
rtf_assemble <- function(path){

@@

}
```

The `rtf_assemble()` function allow you to combine RTF 
source code in individual files into one larger RTF file.

@@

```{r}
rtf_assemble(tlf_path) |> 
  r2rtf::write_rtf("tlf/rtf-combine.rtf")
```

@@

The `rtf_assemble()` function 
allow you to create a word file with toggle fields as below.

>>>>

<details>
<summary>`rtf_assemble1()` source code</summary>
```{r}
#' Assemble RTF files into one single RTF file 
#' 
#' @param path a vector of RTF file path
#' 
#' @export
rtf_assemble1 <- function(path){

@@

}
```
</details>

The `rtf_assemble1()` function allow you to combine RTF 
source code in individual files into one larger RTF file.

@@

```{r}
rtf_assemble1(tlf_path) |> 
  r2rtf::write_rtf("tlf/rtf-combine.rtf")
```

@@

<details>
<summary>`rtf_assemble2()` source code</summary>
```{r}
#' Assemble RTF TLFs
#'
#' Add a set of RTF/TEXT fields into an rdocx object.
#'
#' @param input Character vector of file path.
#' @param output Character string to the output file path.
#' @param landscape Logical vector to determine whether to
#' display files as portrait or landscape.
#'
#' @export
rtf_assemble2 <- function(input, output, landscape = FALSE) {

  input <- normalizePath(input)

  if (!all(file.exists(input))) {
    warning("Some files do not exist")
  }

  field <- ifelse(grepl("/", input),
    paste0("INCLUDETEXT \"", gsub("/", "\\\\\\\\", input), "\""),
    paste0("INCLUDETEXT \"", gsub("\\", "\\\\", input, fixed = "TRUE"), "\"")
  )

  if (length(landscape) == 1) {
    landscape <- rep(landscape, length(field))
  }

  docx <- officer::read_docx()

  for (i in seq_along(input)) {
    docx <-
      docx %>%
      officer::body_add_fpar(
        officer::fpar(
          officer::ftext("Table "),
          officer::run_word_field("SEQ Table \\* ARABIC"),
          officer::run_linebreak(),
          officer::run_word_field(field[i]),
          officer::run_pagebreak()
        )
      )
    if (landscape[i]) {
      docx <- officer::body_end_section_landscape(docx)
    } else {
      docx <- officer::body_end_section_portrait(docx)
    }
  }

  print(docx, target = output)

  invisible(output)
}
```
</details>

The `rtf_assemble2()` function 
allow you to create a word file with toggle fields as below.
One benefit is to control the page direction of each TLF as below.

```{r}
rtf_assemble2(tlf_path, 
              output = "tlf/rtf-combine-toggle.docx", 
              landscape = c(FALSE, FALSE, TRUE))
```
